### 2024-10-09 exposeBerlin2410/exposeBerlin2410.tex
expose Berlin

% COMMANDE DE PARTIE
%\newcounter{partie}
%\setcounter{partie}{1}
%\newcommand{\thePartie}{Part \arabic{partie}}
\newcommand{\partie}[1]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.9\textwidth}{0.5 pt} \\[.5cm]
\fontsize{30}{30}\selectfont {\blue\uppercase{#1}} \\[-.35cm]
\rule{.9\textwidth}{0.5 pt} \\
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

@@

% specific wiggly
\newcommand{\polytope}[1]{\mathds{#1}} % font polytope
\newcommand{\wigglyComplex}{\mathrm{WC}} % wiggly complex
\newcommand{\wigglyFlipGraph}{\mathrm{WFG}} % wiggly flip graph
\newcommand{\wigglyIncreasingFlipGraph}{\mathrm{WIFG}} % wiggly increasing flip graph
\newcommand{\wigglyLattice}{\mathrm{WL}} % wiggly lattice
\newcommand{\wigglyFan}{\mathrm{WF}} % wiggly fan
\newcommand{\wigglyhedron}{\polytope{W}} % wigglyhedron
\newcommand{\Asso}{\polytope{A}\mathsf{sso}} % associahedron

@@

@@

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures0}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\bigskip
\begin{center}
\begin{tabular}{rl}
\emph{triangulation} & = maximal crossing-free set of edges \\
\vspace{.3cm}
\\

\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
\vspace{.3cm}
\\

\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
\\
\end{tabular}
\end{center}
\end{slide}

@@

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures1}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\bigskip
\begin{center}
\begin{tabular}{rl}
\emph{triangulation} & = maximal crossing-free set of edges \\
\vspace{.3cm}
\\

\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
\vspace{.3cm}
\\

\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
\\
\end{tabular}
\end{center}
\end{slide}

@@

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures2}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\bigskip
\begin{center}
\begin{tabular}{rl}
\emph{triangulation} & = maximal crossing-free set of edges \\
\vspace{.3cm}
& = decomposition into triangles \\

\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
\vspace{.3cm}
& = decomposition into pseudotriangles \\

\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
& = decomposition into $k$-stars
\end{tabular}
\end{center}

\vspace{.2cm}
\papier{VP \& F. Santos, Multitriangulations as complexes of star polygons, 2009.}

@@

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures3}\end{center}
\vspace{-8cm} \hspace*{25.7cm} ${k=2}$

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
\begin{center}
\begin{tabular}{r@{\quad $\longleftrightarrow$ \quad}l}
\emph{associahedron} & crossing-free sets of internal edges \\
\emph{pseudotriangulations polytope} & pointed crossing-free sets of internal edges \\
{\red multiassociahedron} & $(k+1)$-crossing-free sets of $k$-internal edges
\end{tabular}
\end{center}

%\begin{slide}{Three geometric structures}
%\vspace{-.8cm}
%\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
%\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
%
%\vspace{-.7cm}
%\begin{flushright}
%``Our main limits in understanding the combinatorial structure of polytopes still\\
%lie in our ability to raise the good questions and in the \emph{lack of examples},\\
%\emph{methods of constructing them}, and \emph{means of classifying them}.'' \\
%\papier{G. Kalai, \emph{Handbook of Discrete \& Computational Geometry}.}
%\end{flushright}
%
%\vspace{-2cm}
%\end{slide}

@@

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures6}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$

\vspace{7.6cm}
\papier{VP \& M. Pocchiola, Multitriangulations, pseudotriangulations and primitive sorting networks, 2012.}

@@

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations

\vspace{1.3cm}
\begin{center}\includegraphics[scale=1.9]{geometricStructures8}\end{center}
\vspace{-8.33cm} \hspace*{25.7cm} ${k=2}$
\end{slide}

@@

\vspace{.1cm}
\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells.}

@@

\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed.}

@@

\vspace{.5cm}
\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected.}

@@

\theo{PROP}{
The cover graph of the lattice~$\wigglyLattice_n$ is $(2n-1)$-regular and connected.
}
\end{minipage}

\vspace{5cm}
\[
\begin{array}{c|ccccccccc}
n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
\hline
wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
\end{array}
\]

@@

\begin{slide}{Bijection}

@@

\vspace{1cm}
\theo{PROP}{The wiggly pseudotriangulations and wiggly permutations are in bijection.}

@@

@@

\begin{slide}{Bijection}

\theo{PROP}{This bijection induces a directed graph isomorphism between
\begin{compactitem}
\item the wiggly increasing flip graph on wiggly pseudotriangulations,
\item the Hasse diagram of the wiggly lattice on wiggly permutations.
\end{compactitem}
}

@@

\vspace{.5cm}
\theo{PROP}{For any wiggly pseudotriangulation~$T$, the $\b{g}$-vectors~$\set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and the $\b{c}$-vectors~$\set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases.}

@@

\vspace{.1cm}
\theo{THM}{The cones~$\setangle{\b{g}(\alpha)}{\alpha \in D}$ for all wiggly dissections~$D$ form a complete simplicial fan~$\wigglyFan_n$ (in $\sum_{i = 1}^{2n} x_i = 0$).
}

@@

\theo{THM}{
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \emph{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item intersection of the halfspaces~$\set{\b{x} \in \R^{2n}}{\dotprod{\b{g}(\alpha)}{\b{x}} \!\le\! \kappa(\alpha)}$ for all wiggly arcs~$\alpha$,
\item convex hull of~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}
\vspace{-.5cm}
}

\vspace{1cm}
\centerline{\input{figures/wigglyhedron}}

@@

\theo{THM}{The wigglyhedron~$\wigglyhedron_n$ is a simple $(2n-1)$-dimensional polytope such that
\begin{compactitem}
\item the wiggly complex~$\wigglyComplex_n$ is the boundary complex of the polar of~$\wigglyhedron_n$,
\item the Hasse diagram of the wiggly lattice is a linear orientation of the graph of~$\wigglyhedron_n$.
\end{compactitem}
}

@@

\vspace{.5cm}
\centerline{\includegraphics[scale=1.6]{wigglyCambrian2}}

@@

\vspace{.5cm}
\centerline{\includegraphics[scale=1.6]{wigglyCambrian3}}

>>>>

% COMMANDE DE PARTIE
%\newcounter{partie}
%\setcounter{partie}{1}
%\newcommand{\thePartie}{Part \arabic{partie}}
\newcommand{\partie}[1]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.9\textwidth}{0.5 pt} \\[.5cm]
\fontsize{30}{30}\selectfont {\blue \uppercase{#1}} \\[-.35cm]
\rule{.9\textwidth}{0.5 pt} \\
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

@@

% specific wiggly
\newcommand{\polytope}[1]{\mathds{#1}} % font polytope
\newcommand{\wigglyComplex}{\mathrm{WC}} % wiggly complex
\newcommand{\wigglyFlipGraph}{\mathrm{WFG}} % wiggly flip graph
\newcommand{\wigglyIncreasingFlipGraph}{\mathrm{WIFG}} % wiggly increasing flip graph
\newcommand{\wigglyLattice}{\mathrm{WL}} % wiggly lattice
\newcommand{\wigglyFan}{\mathrm{WF}} % wiggly fan
\newcommand{\wigglyhedron}{\polytope{W}} % wigglyhedron
\newcommand{\Asso}{\polytope{A}\mathsf{sso}} % associahedron
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\HS}{\b{H}^\ge} % half-space

@@

\begin{slide}{ASSOCIAHEDRON}

\gboite{
\emph{Associahedron} = polytope whose face lattice is isomorphic to the lattice of crossing-free sets of internal diagonals of a convex $(n+3)$-gon, ordered by reverse inclusion
}

\vspace{.2cm}
\centerline{\includegraphics[scale=3.1]{associahedron}}
\vspace*{-3.5cm}
\begin{tabular}{r@{ $\leftrightarrow$ }l}
vertices & triangulations \\
edges & flips \\
faces & dissections
\end{tabular}
\hfill
\begin{tabular}{r@{ $\leftrightarrow$ }l}
vertices & binary trees \\
edges & rotations \\
faces & Schr\"oder trees
\end{tabular}

%%%%%%%%%%
%
%\begin{slide}{VARIOUS ASSOCIAHEDRA}
%
%\gboite{
%\emph{Associahedron} = polytope whose face lattice is isomorphic to the lattice of crossing-free sets of internal diagonals of a convex $(n+3)$-gon, ordered by reverse inclusion
%}
%
%\vspace{.5cm}
%\centerline{\includegraphics[width=\textwidth]{manyAssociahedra1}}
%\vspace{.5cm}
%\centerline{\includegraphics[width=\textwidth]{manyAssociahedra2}}
%
%\vspace{-.2cm}
%\hfill {\normalsize (Pictures by Ceballos-Santos-Ziegler)}
%
%\vspace{-.9cm}
%\papier{
%
%Tamari ('51) --- Stasheff ('63) --- Haimann ('84) --- Lee ('89) --- \hspace*{12.5cm} \\[.2cm]
%\dots --- Gel'fand-Kapranov-Zelevinski ('94) --- \dots --- Chapoton-Fomin-Zelevinsky ('02) --- \dots --- Loday ('04) --- \dots \hspace*{1.5cm} \\[.2cm]
%--- Ceballos-Santos-Ziegler ('11)
%
%}
%
%\end{slide}

\begin{slide}{THREE FAMILIES OF REALIZATIONS}

\vspace{-.25cm}
\hspace{-1.2cm}
\begin{tabular}{cc|ccc|cc}
\begin{minipage}[t]{8.5cm}
\begin{center}
{\blue SECONDARY} \\ {\blue POLYTOPE} \\[.5cm]
\end{center}
\vspace{-.2cm}
\centerline{\includegraphics[scale=1.5]{associahedron}}
\vspace{.1cm}
\papier{Gelfand--Kapranov--Zelevinsky ('94) \\ Billera--Filliman--Sturmfels ('90)

}
\vspace{8cm}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\begin{center}
{\blue LODAY'S ASSOCIAHEDRON} \\[.5cm]
\end{center}
\vspace{-.2cm}
\centerline{\includegraphics[scale=.78]{associahedronLoday}}
\vspace{-.4cm}
\papier{Loday ('04) \\ Hohlweg--Lange ('07) \\ Hohlweg--Lange--Thomas ('12) \\ Hohlweg--Pilaud--Stella ('18) \\ Pilaud--Santos--Ziegler ('24)

}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\begin{center}
{\blue CHAP.--FOM.--ZEL.'S ASSOCIAHEDRON} \\[.5cm]
\end{center}
\centerline{\input{figures/associahedronCFZ}}
\vspace{-7.5cm}\hspace{5.3cm}
{\normalsize (Pictures by CFZ)}
\vspace{5.8cm}

\papier{Chapoton--Fomin--Zelevinsky ('02) \\ Ceballos--Santos--Ziegler ('11)

}
\end{minipage}
\end{tabular}

\begin{slide}{THREE FAMILIES OF REALIZATIONS}

\vspace{-.25cm}
\hspace{-1.2cm}
\begin{tabular}{cc|ccc|cc}
\begin{minipage}[t]{8.5cm}
\begin{center}
{\blue SECONDARY} \\ {\blue POLYTOPE} \\[.5cm]
\end{center}
\vspace{-.2cm}
\centerline{\includegraphics[scale=1.5]{associahedron}}
\vspace{.1cm}
\papier{Gelfand--Kapranov--Zelevinsky ('94) \\ Billera--Filliman--Sturmfels ('90)

}
\vspace{.1cm}
\centerline{\includegraphics[scale=1.5]{secondaryPolytope}}
\vspace{1cm}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\begin{center}
{\blue LODAY'S ASSOCIAHEDRON} \\[.5cm]
\end{center}
\vspace{-.2cm}
\centerline{\includegraphics[scale=.78]{associahedronLoday}}
\vspace{-.4cm}
\papier{Loday ('04) \\ Hohlweg--Lange ('07) \\ Hohlweg--Lange--Thomas ('12) \\ Hohlweg--Pilaud--Stella ('18) \\ Pilaud--Santos--Ziegler ('24)

}
\vspace{.3cm}
\hspace{-.4cm}\boxed{\begin{minipage}{2.5cm} \smallskip \begin{center} \blue Hopf \\ algebra \\[-1.2cm] ~\end{center} \end{minipage}} \\[.2cm]
\hspace*{-.4cm}\boxed{\begin{minipage}{2.5cm} \smallskip \begin{center} \blue Cluster \\ algebras \\[-1.2cm] ~\end{center} \end{minipage}} \\
\vspace{-4.7cm}
\hspace*{3.5cm}\includegraphics[scale=.35]{associahedronTypeB}
\vspace{-.2cm}
\hspace*{2.5cm}\includegraphics[scale=.35]{associahedronTypeH}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\begin{center}
{\blue CHAP.--FOM.--ZEL.'S ASSOCIAHEDRON} \\[.5cm]
\end{center}
\centerline{\input{figures/associahedronCFZ}}
\vspace{-7.5cm}\hspace{5.3cm}
{\normalsize (Pictures by CFZ)}
\vspace{5.8cm}

\papier{Chapoton--Fomin--Zelevinsky ('02) \\ Ceballos--Santos--Ziegler ('11)

}
\vspace{1.2cm}
\hspace{-.4cm}\boxed{\begin{minipage}{2.5cm} \smallskip \begin{center} \blue Cluster \\ algebras \\[-1.2cm] ~\end{center} \end{minipage}} \\
\vspace{-3cm}
\centerline{\hspace{2.5cm}\input{figures/cyclohedronCFZ}}

\end{minipage}
\end{tabular}

%%%%%%%%%
%
%\begin{slide}{LODAY'S ASSOCIAHEDRON}
%
%\vspace{-.3cm}
%\cboite{
%\vspace{-.7cm}
%\[
%\Asso(n) \, \eqdef \, \conv \set{\b{L}(T)}{T \text{ binary tree}} \, = \, \HH \; \cap \!\!\!\!\!\! \bigcap_{1 \le i \le j \le n+1} \!\!\!  \HS(i,j)
%\]
%\vspace{-.3cm}
%\[
%\b{L}(T) \eqdef \big[ \ell(T, i) \cdot r(T, i) \big]_{i \in [n+1]}
%\qquad
%\HS(i,j) \eqdef \biggset{\b{x} \in \R^{n+1}}{\sum_{i \le k \le j} x_i \ge \binom{j-i+2}{2} \!\! }
%\]
%
%\flushright{
%\papier{
%	Shnider-Sternberg, \textit{Quantum groups: From coalgebras to Drinfeld algebras} ('93) \\
%	Loday, \textit{Realization of the Stasheff polytope} ('04)
%	
%}}
%}
%
%\vspace{.3cm}
%\centerline{\raisebox{1cm}{\includegraphics[scale=2.2]{LodayVector}} \qquad  \includegraphics[scale=1.15]{associahedronLoday}}
%
%\end{slide}
%
%%%%%%%%%

\begin{slide}{LODAY'S ASSOCIAHEDRON}

\vspace*{-1cm}
\begin{align*}
\text{\blue Loday's associahedron} \; & = \; \conv \set{L(T)}{T \text{ triangulation of the } (n+3)\text{-gon}} \\
& = \; \HH \; \cap \!\!\!\!\! \bigcap_{\substack{\delta \text{ diagonal} \\ \text{of the } (n+3)\text{-gon}}} \!\!\!\!\!\!\!\!\!\! \HS(\delta)
\end{align*}

\vspace{-.5cm}
\centerline{
	\begin{overpic}[scale=2.5]{lodayTriangulation}
		\put(30,90){$i$}
		\put(175,0){$j$}
		\put(345,175){$k$}
		\put(53,23){$\ell(T,j)$}
		\put(295,55){$r(T,j)$}
		\put(560,140){$\delta$}
		\put(595,5){$B(\delta)$}
   \end{overpic}
}
\[
\hspace{1.8cm}
L(T) = \big(\ell(T,j) \, \cdot \, r(T,j)\big)_{j \in [n+1]}
\hspace{1.7cm}
\HS(\delta) = \biggset{\b{x} \in \R^{n+1}}{\sum_{j \in B(\delta)} x_j \ge \binom{|B(\delta)|+1}{2}}
\]

\vspace{.5cm}
\papier{Loday ('04)}

\begin{slide}{HOHLWEG \& LANGE'S ASSOCIAHEDRA}

Can also replace Loday's $(n+3)$-gon by others\dots

\vspace{.2cm}
\centerline{\includegraphics[width=\textwidth]{polygonsHohlwegLange}}

\vspace{-.3cm}
\dots to obtain different realizations of the associahedron

\vspace{.1cm}
\centerline{\includegraphics[scale=2]{associahedronLodayHL}}

\vspace{-.6cm}
\papier{Hohlweg--Lange ('07)}

\begin{slide}{HOHLWEG \& LANGE'S ASSOCIAHEDRA}

\vspace*{-1cm}
\[
\Asso(P) \; = \; \conv \set{H\!L(T)}{T \text{ triangulation of } P} \; = \; \HH \; \cap \!\!\!\!\! \bigcap_{\delta \text{ diagonal of } P} \!\!\!\!\!\!\!\!\!\! \HS(\delta)
\]

\vspace{-.6cm}
\centerline{
	\begin{overpic}[scale=2.5]{hohlwegLange}
		\put(30,85){$i$}
		\put(85,325){$j$}
		\put(255,30){$k$}
		\put(-20,225){$\ell(T,j)$}
		\put(275,290){$r(T,j)$}
		\put(540,165){$\delta$}
		\put(370,110){$B(\delta)$}
   \end{overpic}
}

\vspace{-1.3cm}
\[
\hspace*{-1cm}
H\!L(T)_j =
\begin{cases}
	\ell(T,j) \cdot r(T,j) & \text{if } j \text{ down} \\
	n+2-\ell(T,j) \cdot r(T,j) & \text{if } j \text{ up}
\end{cases}
\hspace{1.4cm}
\HS(\delta) = \biggset{\b{x}}{\sum_{j \in B(\delta)} x_j \ge \binom{|B(\delta)|+1}{2}}
\]

\papier{Hohlweg--Lange ('07)}

@@

\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures0}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\hspace{1.7cm} 
\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\  \end{tabular} 
\hspace{3.4cm} 
\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\  \end{tabular}
\hspace{2cm} 
\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ \\  \end{tabular}

@@

\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures1}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\hspace{1.7cm} 
\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\  \end{tabular} 
\hspace{3.4cm} 
\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\  \end{tabular}
\hspace{2cm} 
\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ \\  \end{tabular}

@@

\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures2}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\hspace{1.7cm} 
\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\ triangles \end{tabular} 
\hspace{3.4cm} 
\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\ pseudotriangles \end{tabular}
\hspace{2cm} 
\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ $k$-stars \\ \papier{P.--Santos ('09)} \end{tabular}

\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures3}\end{center}
\vspace{-8cm} \hspace*{25.7cm} ${k=2}$

\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
\hspace{1.5cm} associahedron \hspace{2.6cm} pseudotriangulation polytope \hspace{1.2cm} multiassociahedron

@@

%\begin{slide}{Three geometric structures}
%\vspace{-.8cm}
%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
%\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
%
%\vspace{-.7cm}
%\begin{flushright}
%``Our main limits in understanding the combinatorial structure of polytopes still\\
%lie in our ability to raise the good questions and in the \emph{lack of examples},\\
%\emph{methods of constructing them}, and \emph{means of classifying them}.'' \\
%\papier{G. Kalai, \emph{Handbook of Discrete \& Computational Geometry}.}
%\end{flushright}
%
%\vspace{-2cm}
%\end{slide}

@@

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures6}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$

\vspace{7.6cm}
\papier{P.--Pocchiola ('12)}

@@

%%%%%%%%%%
%
%\begin{slide}{Duality}
%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
%
%\vspace{1.3cm}
%\begin{center}\includegraphics[scale=1.9]{geometricStructures8}\end{center}
%\vspace{-8.33cm} \hspace*{25.7cm} ${k=2}$
%\end{slide}

@@

\vspace{.1cm}
\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\vspace{.5cm}
\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\hfill \papier{Bapat--P. (24$^+$)}
}

\theo{PROP}{
The cover graph of the lattice~$\wigglyLattice_n$ is $(2n-1)$-regular and connected.

\hfill \papier{Bapat--P. (24$^+$)}
}
\end{minipage}

\vspace{3cm}
\[
\begin{array}{c|ccccccccc}
n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
\hline
wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
\end{array}
\]

@@

\begin{slide}{Wiggly pseudotriangulations $\longleftrightarrow$ wiggly permutations}

@@

\vspace{1cm}
\theo{PROP}{The wiggly pseudotriangulations and wiggly permutations are in bijection.

\hfill \papier{Bapat--P. (24$^+$)}
}

@@

{\color{gray}
permutation of $2n$ avoiding \begin{tabular}[t]{@{}l} $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$ \\ $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$ \end{tabular}}

@@

\begin{slide}{Wiggly pseudotriangulations $\longleftrightarrow$ wiggly permutations}

\theo{PROP}{This bijection induces a directed graph isomorphism between
\begin{compactitem}
\item the wiggly increasing flip graph on wiggly pseudotriangulations,
\item the Hasse diagram of the wiggly lattice on wiggly permutations. \hfill \papier{Bapat--P. (24$^+$)}
\end{compactitem}
}

@@

\vspace{.5cm}
\theo{PROP}{For any wiggly pseudotriangulation~$T$, the $\b{g}$-vectors~$\set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and the $\b{c}$-vectors~$\set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\vspace{.1cm}
\theo{THM}{The cones~$\setangle{\b{g}(\alpha)}{\alpha \in D}$ for all wiggly dissections~$D$ form a complete simplicial fan~$\wigglyFan_n$ (in $\sum_{i = 1}^{2n} x_i = 0$). \hfill \papier{Bapat--P. (24$^+$)}
}

@@

\theo{THM}{
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \emph{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item intersection of the halfspaces~$\set{\b{x} \in \R^{2n}}{\dotprod{\b{g}(\alpha)}{\b{x}} \!\le\! \kappa(\alpha)}$ for all wiggly arcs~$\alpha$,
\item convex hull of~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}

\vspace{-.6cm}
\hfill \papier{Bapat--P. (24$^+$)}
}

\vspace{.5cm}
\centerline{\input{figures/wigglyhedron}}

@@

\theo{THM}{The wigglyhedron~$\wigglyhedron_n$ is a simple $(2n-1)$-dimensional polytope such that
\begin{compactitem}
\item the wiggly complex~$\wigglyComplex_n$ is the boundary complex of the polar of~$\wigglyhedron_n$,
\item the Hasse diagram of the wiggly lattice is a linear orientation of the graph of~$\wigglyhedron_n$.
\end{compactitem}

\hfill \papier{Bapat--P. (24$^+$)}
}

@@

\theo{THM}{
For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between 
\begin{compactitem}
\item $\delta$-triangulations
\item $\delta$-permutations
\item $\delta$-wiggly pseudotriangulations
\item $\delta$-wiggly permutations \hfill \papier{Bapat--P. (24$^+$)}
\end{compactitem}
}

\vspace{.5cm}
\centerline{\includegraphics[scale=1.5]{wigglyCambrian2}}

@@

\theo{THM}{
For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between 
\begin{compactitem}
\item $\delta$-triangulations
\item $\delta$-permutations
\item $\delta$-wiggly pseudotriangulations
\item $\delta$-wiggly permutations \hfill \papier{Bapat--P. (24$^+$)}
\end{compactitem}
}
